Generating Images From Captions

### 2015-10-09 ram_workshop/ram-paper.tex

\maketitle
\vspace*{-0.4cm}
\begin{abstract}
\vspace*{-0.15cm}
Images rarely appear in isolation as they are often accompanied by textual description that could be used to simplify image generation. In this work, we introduce a model that iteratively draws patches on a canvas, while attending to the relevant words in the description. After training on COCO, we illustrate how our model generalizes to captions describing novel scenarios that are not seen in the dataset.
\end{abstract}

>>>>

\maketitle
\vspace*{-0.4cm}
\begin{abstract}
\vspace*{-0.15cm}
Motivated by the recent progress in generative models, we introduce a model that generates images from natural language descriptions. The proposed model iteratively draws patches on a canvas, while attending to the relevant words in the description. After training on MSCOCO, we compare our models with several baseline generative models on image generation and retrieval tasks. We then demonstrate our model produces higher quality samples than other approaches and generates images with novel scene compositions corresponding to previously unseen captions in the dataset.   
\end{abstract}
